The imprint of global magma oceans on exoplanet demographics

### 2022-11-28 src/tex/ms.tex
describe choice of eccentricities, inclinations

\subsubsection{Eccentricities, orbital inclinations, and planet masses}

>>>>

\subsubsection{Eccentricities, orbital inclinations, and planet masses}
Eccentric orbits alter the probability of a planet to transit \citep[e.g.,][]{Barnes2007a}.
The distribution of eccentricities $e$ of exoplanets has been found to resemble a Beta function \citep{Kipping2013b}, which we chose to draw synthetic eccentricities from.
Following~\citet{Kipping2013b}, we used a Beta distribution with parameters $a=0.867$ and $b=3.03$, and truncated the distribution at $e = 0.8$.

Another parameter with an even higher impact on transit probabilities is the orbital inclination toward the observer $i$.
Assuming isotropic alignments of orbits, we assigned each planet an inclination drawn from a distribution uniform in $\cos(i)$.
